An Algorithmic Introduction to Lagrangian Coherent Structures

### 2014-01-30 main.tex
Modify and expand abstract

\abstract{
We give an applied introduction to Lagrangian coherent structures (LCSs.) We review recent results in variational LCS theory, present algorithms based on the theory and implement the algorithms in a computational engine called LCS Tool. We use LCS Tool to analyse flow examples.
}

>>>>

\abstract{
We give an applied introduction to Lagrangian coherent structure (LCS) detection. We review LCS theory that is based on variational calculus, present algorithms conceived in accordance with the variational theory and present a MATLAB computational engine called LCS Tool that enables variational LCS calculations and detection. We use LCS Tool to analyse three flow examples: a double gyre, a Bickley jet and an ocean dataset.
}
